{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2021-11-23 pheno.tex
Updating 7.5

%%%
\subsection{$b \to s\gamma$}
%%%
The  quark level process $b \to s\gamma$ is a Flavour Changing Neutral Current (FCNC) process which must proceed through loops in the Standard Model since there are no tree-level FCNC interactions there. At meson level it leads to measurable decays of the type $B\to X_s\gamma$, where $X_s$ is some meson with a strange quark, {\it e.g.}\  the decay $B\to K\gamma$. Figure~\ref{btosdiags} a) shows the one-loop Standard Model contribution with a virtual $W$ and up-type quarks. This contribution is suppressed by the smallness of the CKM entries in the $W$-vertices, and the large masses, $M_W$ and $m_t$, in the loop.

>>>>

%%%
\subsection{$b \to s\gamma$}
%%%
The  quark level process $b \to s\gamma$ is a Flavour Changing Neutral Current (FCNC) process which must proceed through loops in the Standard Model since there are no tree-level FCNC interactions there. At meson level it leads to measurable decays of the type $B\to X_s\gamma$, where $X_s$ is some meson with a strange quark, {\it e.g.}\  the decay $B\to K\gamma$. Figure~\ref{btosdiags} a) shows the one-loop Standard Model contribution with a virtual $W$ and up-type quarks. This contribution is suppressed by the smallness of the CKM entries in the $W$-vertices which favours diagrams with a top quark in the loop, and the large masses, $M_W$ and $m_t$, in the loop.
